\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex

\section{Background \& Significance}

@@

\section{Expected Outcomes}
Words

\section{Conclusions}
Words

>>>>

\section{Background \& Significance}
Throughout history, people have tried to gain access restricted areas. \cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.  The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.  Bramah had just developed his so called safety lock.  His lock had safety features that he believed to be completely secure.  Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.  Anyone who could break into his new creation would net a cool sum of 20,000 pounds.

While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.  Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.  He too, announced a challnge.  An American Locksmith named A.C. Hobbs took up the challenge, and had it open within an hour of touching the lock.  However, that wasn't the only challenge he accepted.  Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.

New technology leads to new innovation.  Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.  Granting access to a building is as simple as a few button clicks.  For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.

Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.  With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.  These locks aren't invulnerable, and security professionals can certainly help bring them to the point where they can withstand basic attacks.

@@

\section{Expected Outcomes}
Not every penetration test finds a massive zero day vulnerability.  However, that doesn't mean a test isn't completely useless.  Tests may not often discover massive issues, but smaller issues are often prevalent.  Issues such as weaker cryptography, issues with bad hardware intrusion detection, and bad endpoint security on older protocols are commonplace.  It should be expected to find several smaller issues rather than major flaws in the firmware or the device itself.

Overall, we expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.  Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.

\section{Conclusions}
Throughout this paper, we have discussed how to design a testing framework for attacking modern electronic locking technologies.  We listed out different types of attacks that could be run against a bluetooth-enabled locking solution.  Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.

We also discussed attacking the device from the backend, from the protocols that allow for the lock to communicate securely with an authentication server.  This includes the Wiegand protocol, which is not designed with a security focus in mind.

Lock picking may not yet be on the decline, but electronic locking mechanisms allow for greater viability for most organizations. Overall, electronic locking solutions will be used far into the future.  It's heavily important to test these locks to verify that the cryptographic and security mechanisms of these locks are structurally sound.
